Implementing Adaptive Beamforming on the GPU for Real Time Ultrasound Imaging

### 2012-04-23 SiPS2012/sips2012.tex
Done some wrighting on the sips/ius/uffc article

@@

\section{Method}\label{sec:meth}
\subsection{Building the Sample Covariance Matrix}
Building $\hat{\mat{R}}$ using a sliding window approach across $K$ and $N_{avg}$. We have a limited amount of fast, near-core memory on the GPU. On NVIDIA architecture this memory is known as shared memory, and is restricted to 48KB per compute block. The maximum block size of 32x32, further restrict how large arrays we can handle inside a single compute block. We therefore restrict $L$ to a maxima of $32$ elements. Since $L \le M/2$, $M \le 64$. We can not afford to hold the full $\hat{\mat{R}}$ ($M = L$) when $\hat{\mat{R}} > 32$, because of limitied amount of memory. ... Explain in detail how \texttt{buildR} is implemented in a kernel. ... Give more details on how much shared memory we have, and how it can be divided between compute blocks occupying one stream multiprocessor (SM).

@@

>>>>

Finally, $\mat{\hat{R}}$ is loaded with diagonal factor $\epsilon$, $\mat{\hat{R}} = \mat{\hat{R}} + \epsilon\mat{I}$. A weighting proportional to the output power is beneficial, and the trace of $\mat{\hat{R}}$, $\epsilon = d*tr\{\mat{\hat{R}}\}$, has previously shown good results in the literature (cite).

@@

\section{Method}\label{sec:meth}
\subsection{Building the Sample Covariance Matrix}
Building $\hat{\mat{R}}$ using a sliding window approach across $K$ and $N_{avg}$. We have a limited amount of fast, near-core memory on the GPU. On NVIDIA architecture this memory is known as shared memory, and is restricted to 48KB per compute block. The maximum block size of 32x32, further restrict how large arrays we can handle inside a single compute block. It is therefore natural to restrict $L$ to a maxima of $32$ elements. Since $L \le M/2$, $M \le 64$. We can not afford to hold the full $\hat{\mat{R}}$ ($M = L$) when $\hat{\mat{R}} > 32$, because of limited amount of memory. ... Explain in detail how \texttt{buildR} is implemented in a kernel. ... Give more details on how much shared memory we have, and how it can be divided between compute blocks occupying one stream multiprocessor (SM).

Discuss the bottleneck adaptive diagonal loading causes.

Time averaging takes a lot of resources. It has been shown that time averaging can maintain both resolution and delay-and-sum-like speckle. The same speckle statistics can be obtain with small subarrays, but then we loose resolution. Small sub-arrays benefits from being less computational demanding.

@@

In the final journal article we could discuss Conjugated gradient and Woodbury and the benefits they bring.
